An introduction to the \texttt{metafolio} \texttt{R} package

### 2013-10-26 vignette/metafolio.Rnw
Minor vignette edits

The main simulation function is \texttt{meta\_sim}. We'll start by running a
simulation using the base-case parameter values from the paper. First, we'll
set up a list object that contains the argument values for the stationary
environmental stochasticity scenario. The arguments \texttt{mean\_value},
\texttt{ar}, and \texttt{ma} refer to the mean, autoregressive (AR), and
moving-average (MA) components of an ARIMA model. See \texttt{?arima} for
further explanation of ARIMA models in R. The argument \texttt{sigma\_env}
refers to the standard deviation of the environmental signal.

@@

@@

One of the key elements to the analysis in our paper is the choice of
which populations to prioritize for conservation. We can try different
prioritization strategies by manipulating the ``investment weights'' in each
stream of salmon. In the case of salmon, we represent these with the Ricker
$b_i$ parameters, which represent the maximum population capacity of streams
$i$ 1 through $n$.

>>>>

The main simulation function in \texttt{metafolio} is
\texttt{meta\_sim}. We'll start by running a simulation using the base-case
parameter values from the paper. First, we'll set up a list object that
contains the argument values for the stationary environmental stochasticity
scenario.

@@

The arguments \texttt{mean\_value}, \texttt{ar}, and \texttt{ma} refer to
the mean, autoregressive (AR), and moving-average (MA) components of an
ARIMA model. See \texttt{?arima} for further explanation of ARIMA models in
R. The argument \texttt{sigma\_env} refers to the standard deviation of the
environmental signal.

@@

One of the key elements to the analysis in our paper is the choice of
which populations to prioritize for conservation. We can try different
prioritization strategies by manipulating the ``investment weights'' in each
stream of salmon. In the case of salmon, we represent these with the Ricker
$b_i$ parameters, which indicate the maximum population capacity of streams
$i$ 1 through $n$.
